---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mycoBinR

<!-- badges: start -->
<!-- badges: end -->

The goal of mycoBinR is to is to organize and manage file paths for outputs generated by a Snakemake pipeline, simplifying downstream data processing for fungal genome projects.

## Installation

You can install the development version of mycoBinR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("taui11/mycoBinR")
```

## Example

The `create_filepaths_df()` function builds a data frame listing the file names and their paths for a given project directory, project number, and project title.

```{r example}
library(mycoBinR)

filepaths <- create_filepaths_df(
  base_path = "/project/data_output",
  project_nr = "pr_01_",
  TITLE = "001"
)
print(filepaths)
```
